---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hei

<!-- badges: start -->
<!-- badges: end -->

Healthy Eating Index (HEI) scoring is not the simplest of calculations. This package contains a function to compute HEI total and component scores from ASA 24-hour diet recall data.


## Installation

You can install the released version of hei from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("hei")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AdamSadowski/hei")
```



## Quick demo

Adding HEI columns to the end of a data frame via `hei()`:

1) Example data:

```{r example}
library(hei)

asa.df <- read.csv(".\\tests\\testthat\\asa_example_df.csv")

asa.df
```

2) `hei()` creates HEI variables for each row. It accepts a data frame and returns it with these added variables. 

```{r}
df <- hei(asa.df)

# grep just to show X and HEI variables

df[, grep("X|HEI", names(df))]

```
